---
title: "Case Study: MovieMagic Concessions and User Review Statistical Analysis"
author: "Brian Burdick, Chris Gearheart and Chris Porter"

output:
  html_document: default
  pdf_document: default
---
```{r setup, include= FALSE}
# Install Libraries
library(dplyr)

# Load project data
data <- read.csv("http://data.mishra.us/files/project_data.csv")
text <- read.csv(url("http://data.mishra.us/files/project_reviews.csv"))
```

##  Introduction

A movie chain in the southwest region, *MovieMagic*, is considering ways in which it can
increase spending on concessions. It has collected information of 2000 of its customers,
some of whom are part of their loyalty program and some who are not. They have
information on 8 variables, which they plan to use as predictors. They
plan to use the amount spent on concessions as the outcome variable
since they have learned from observation that much of their profit is derived from concession
sales.

**Regression analysis**


```{r linear regression, warning=FALSE, message=FALSE}
#head(data)
model1<- lm(amount_spent~., data=data)
summary(model1) # will give output for each level of each categorical predictor

```

**Penalized Regression**

```{r, warning=FALSE, message=FALSE}


```


**Predictive model**
The analysis was run by splitting the data........
```{r, warning=FALSE, message=FALSE}


```

**Text Analysis**

```{r, warning=FALSE, message=FALSE}


```
